---
title: "Raw_Data_Wrangling"
author: "Ryan Waln"
format: html
editor: visual
---

# Introduction

This file will explore the distribution of responses by fishers and non fishers in the raw data through histograms to determine statistical tests to run on them as well as different typologies to create based on the distributions.

```{r, message=FALSE, warning=FALSE, include=FALSE}
# R Setup & housekeeping
knitr::opts_chunk$set(
	echo = TRUE,
	include = TRUE,
	message = FALSE,
	warning = FALSE)

rm(list=ls())
objects()
```

```{r}
# Packages
library("gert")
library("usethis")
library("here")
library("tidyverse")
library("readxl")
```

```{r}
# Import Raw Data sheet
raw_data <- read_excel(here::here("Data/SELTMP-2025-GBR-surveydataset_v1-0_RecFishingCLUSTERS_RyanW-Sept-22-2026.xlsx"), sheet = "Raw_Data")

##glimpse(raw_data)
```

# Histograms for distribution of responses

## Sustainable Practice Support

### Question 11

```{r}
# Histogram for actions taken to help the GBR
raw_data |>
  filter(!is.na(actions_helpGBR)) |>
  ggplot(aes(x = actions_helpGBR)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:5) +
  labs(
    title = "Actions Taken to Help the GBR",
    x = "Rating (1-5)",
    y = "Number of Respondents"
  ) +
  theme_minimal()

```

### Question 14

```{r}
# Histogram for encouraging responsible fishing practices
raw_data |>
  filter(!is.na(GBRbp_advocacyfish)) |>
  ggplot(aes(x = GBRbp_advocacyfish)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Encourage Responsible Fishing Practices",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()

```

```{r}
# Histogram for disposing of rubbish properly
raw_data |>
  filter(!is.na(GBRbp_rubbish)) |>
  ggplot(aes(x = GBRbp_rubbish)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Dispose of Rubish Properly",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()

```

```{r}
# Histogram for reporting sightings on Eye of the Reef App
raw_data |>
  filter(!is.na(GBRbp_app)) |>
  ggplot(aes(x = GBRbp_app)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Report Sightings on EoRA",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()

```

```{r}
# Histogram for reporting suspicious activities to authorities
raw_data |>
  filter(!is.na(GBRbp_report)) |>
  ggplot(aes(x = GBRbp_report)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Report Suspicious Activitiy to the Authorities",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()

```

### Question 19
```{r}
# Histogram for Support of MPAs

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_zoning), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>
  
  # Plot Data
  ggplot(aes(x = inter_zoning)) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:10) +
  
  # Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
  # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Marine Park zoning to restrict certain activities (e.g. fishing, collecting) in some areas of the GBR", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```


```{r}
# Histogram for Support of Fish Closures

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_fishclosures), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_fishclosures)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Seasonal closures for certain fish species (e.g., closures during spawning)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Culling CoTS

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_culling), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_culling)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Culling Crown of Thorns Starfish (a sea star that feeds on coral) to protect corals on reefs", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Coral Restoration

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_coralrestore), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_coralrestore)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Coral restoration (i.e., assisted propagation or ‘gardening’ of corals) to replenish damaged reefs", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Citizen Science Programs

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_citizen), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_citizen)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Community and citizen science programs that involve local people in reef monitoring and clean-ups", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Mangrove & Seagrass Restoration

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_coastrestore), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_coastrestore)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Coastal and inshore restoration (e.g., mangroves, seagrass)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()

```

```{r}
# Histogram for Support of Island Restoration

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_islandrestore), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_islandrestore)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Island rehabilitation and restoration", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Increased Poaching Enforcement

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_illfish), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_illfish)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Surveillance and enforcement to reduce illegal fishing (e.g., poaching in protected Marine Park zones)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Assisted Coral Adaptation

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_coraladapt), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_coraladapt)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Assisted coral adaptation to increase tolerance to rising sea temperatures (e.g., through selective breeding of coral)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Improved Water Quality

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_water), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_water)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Improved land management to reduce sediments and nutrients flowing into the sea", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Reduction in Plastics

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_rubbish), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_rubbish)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Efforts to reduce rubbish and plastics from urban areas entering GBR waters", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Indigenous Rangers

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_indig), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_indig)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Providing support for Indigenous Traditional Owner co-management of the GBR (e.g., Indigenous Rangers, training programs)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Responsible In-Water Recreation

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_rec), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_rec)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap(" Efforts to improve on-water practices by recreational users and tourists (e.g., reducing coral damage from anchors and human contact)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Govt Climate Action

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_carbon), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_carbon)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap(" Government and industry initiatives to reduce carbon emissions and tackle climate change", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Support of Less Invasive Fishing Tech

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_fishing), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_fishing)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Development of new equipment (fishing gear) for commercial fishers to reduce risks to non-target species (e.g., threatened and protected animals)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

### Question 23

```{r}
# Histogram for Understanding how GBR is Managed
raw_data |>
  filter(!is.na(dm_understanding)) |>
  ggplot(aes(x = dm_understanding)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Confidence in Understanding how GBR is Managed",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Belief that GBR is Managed Fairly
raw_data |>
  filter(!is.na(dm_procfair)) |>
  ggplot(aes(x = dm_procfair)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Belief that GBR is Managed Fairly",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Belief that GBR Management Costs are Fairly Distributed
raw_data |>
  filter(!is.na(dm_distfair)) |>
  ggplot(aes(x = dm_distfair)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Belief that GBR Management Costs are Fairly Distributed",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Belief that GBR Management Costs are Fairly Distributed
raw_data |>
  filter(!is.na(dm_distfair)) |>
  ggplot(aes(x = dm_distfair)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Belief that GBR Management Costs are Fairly Distributed",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Belief that GBR Management Respects all Stakeholder Groups
raw_data |>
  filter(!is.na(dm_equity)) |>
  ggplot(aes(x = dm_equity)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Belief that GBR Management Respects all Stakeholder Groups",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Belief that GBRMPA is Trustworthy
raw_data |>
  filter(!is.na(trust_dm)) |>
  ggplot(aes(x = trust_dm)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Belief that GBRMPA is Trustworthy",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Satisfaction in GBR Management
raw_data |>
  filter(!is.na(sat_mgmt)) |>
  ggplot(aes(x = sat_mgmt)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Satisfaction in GBR Management",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Personal Benefit from GBR Management
raw_data |>
  filter(!is.na(benefit_mgmt)) |>
  ggplot(aes(x = benefit_mgmt)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Personal Benefit from GBR Management",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for Belief that GBR Management is well Recognized
raw_data |>
  filter(!is.na(pride_mgmt)) |>
  ggplot(aes(x = pride_mgmt)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Belief that GBR Management is Well Recognized",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

## Environmental Attitudes

### Question 15

```{r}
# Histogram for value of biodiversity the GBR provides
raw_data |>
  filter(!is.na(values_biodiversity)) |>
  ggplot(aes(x = values_biodiversity)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value of GBR Biodiversity",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of GBR existing despite no personal benefits
raw_data |>
  filter(!is.na(values_exist)) |>
  ggplot(aes(x = values_exist)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value of GBR Existing Despite no Personal Benefit",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of passing down traditions related to GBR
raw_data |>
  filter(!is.na(values_bequest)) |>
  ggplot(aes(x = values_bequest)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value of passing down GBR Traditions",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of Tourism
raw_data |>
  filter(!is.na(values_icon)) |>
  ggplot(aes(x = values_icon)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value of GBR Tourism",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of World Heritage Status
raw_data |>
  filter(!is.na(values_recognition)) |>
  ggplot(aes(x = values_recognition)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value of GBR World Heritage Status",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of GBR providing Seafood
raw_data |>
  filter(!is.na(values_provision)) |>
  ggplot(aes(x = values_provision)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value of Seafood from GBR",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of educational opportunities from GBR
raw_data |>
  filter(!is.na(values_science)) |>
  ggplot(aes(x = values_science)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value Educational Opportunities from GBR",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of Traditional Owner Heritage
raw_data |>
  filter(!is.na(values_indigenous)) |>
  ggplot(aes(x = values_indigenous)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value Traditional Owner Heritage of GBR",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of Maritime Heritage
raw_data |>
  filter(!is.na(values_heritage)) |>
  ggplot(aes(x = values_heritage)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value GBR Maritime Heritage",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of GBR Spiritual/Artistic Inspiration
raw_data |>
  filter(!is.na(values_spiritual)) |>
  ggplot(aes(x = values_spiritual)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value GBR Spirtual/Artistic Inspiration",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of GBR supporting local economy
raw_data |>
  filter(!is.na(values_economy)) |>
  ggplot(aes(x = values_economy)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value GBR supporting local economy",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of GBR Recreation
raw_data |>
  filter(!is.na(values_recreation)) |>
  ggplot(aes(x = values_recreation)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value GBR Recreation",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

```{r}
# Histogram for value of GBR providing opportunities to be in nature
raw_data |>
  filter(!is.na(values_ture)) |>
  ggplot(aes(x = values_ture)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  labs(
    title = "Distribution of Responses: Value GBR providing opportunities to be in nature",
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) +
  theme_minimal()
```

## Misinformation

### Question 18

```{r}
# Histogram for certainty that climate change is a threat to the GBR
raw_data |>
  filter(!is.na(cc_belief)) |>
  ggplot(aes(x = cc_belief, fill = factor(cc_belief))) +
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  scale_x_continuous(breaks = 1:6) +
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Threat that needs immediate action",
      "2 = Threat but doesn't need immediate action ",
      "3 = Need more evidence to form an opinion",
      "4 = Not a threat",
      "5 = No view",
      "6 = Don't believe in climate change"
    )
  )
```

