---
title: "Raw_Data_Distribution_FvsNF"
author: "Ryan Waln"
format: html
editor: visual
---

# Introduction

This file will explore the distribution of responses by fishers and non fishers in the raw data through histograms to determine statistical tests to run on them as well as different typologies to create based on the distributions.

```{r, message=FALSE, warning=FALSE, include=FALSE}
# R Setup & housekeeping
knitr::opts_chunk$set(
	echo = TRUE,
	include = TRUE,
	message = FALSE,
	warning = FALSE)

rm(list=ls())
objects()
```

```{r}
# Packages
library("gert")
library("usethis")
library("here")
library("tidyverse")
library("readxl")
```

```{r}
# Import Raw Data sheet
raw_data <- read_excel(here::here("Data/SELTMP-2025-GBR-surveydataset_v1-0_RecFishingCLUSTERS_RyanW-Sept-22-2026.xlsx"), sheet = "Raw_Data")

##glimpse(raw_data)
```

# Histograms for distribution of responses

## Sustainable Practice Support

### Question 11

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for actions taken to help the GBR

# Filter NA values and sort by fisher status
raw_data |> filter(!is.na(actions_helpGBR), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  
  # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data - x and fill now both reference actions_helpGBR (this was the bug)
  ggplot(aes(x = actions_helpGBR, fill = factor(actions_helpGBR))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:5) +
  
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 5),
    labels = c(
      "1 = Yes, as part of a formal or organised group/program",
      "2 = Yes, independently (on my own or as part of an informal group)",
      "3 = Yes, a mix of both",
      "4 = No",
      "5 = Unsure")) +
  
  # Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
  # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("In the last 12 months, have you undertaken any actions to help protect the Great Barrier Reef (GBR; which includes mainland beaches, bays, creeks, islands, open waters, and coral reefs)?", width = 70),
    x = "Responses (1-5)",
    y = "Number of Respondents"
  ) 
```

### Question 14

```{r}
# Histogram for encouraging responsible fishing practices

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(GBRbp_advocacyfish), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = GBRbp_advocacyfish)) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:10) +
  
  # Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
  # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("When you visit the GBR how often do you preform the following actions: Encourage other people to practice responsible fishing (i.e., no fishing in green zones, throw back undersized fish or female mud crabs, follow bag limits)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for disposing of rubbish properly

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(GBRbp_rubbish), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = GBRbp_rubbish)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("When you visit the GBR how often do you preform the following actions: Dispose of food scraps and rubbish appropriately (i.e., in a rubbish bin on shore, not overboard)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for reporting sightings on Eye of the Reef App

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(GBRbp_app), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = GBRbp_app)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("When you visit the GBR how often do you preform the following actions: Report sightings of unusual or interesting marine life using the ‘Eye on the Reef’ sightings network app)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for reporting suspicious activities to authorities

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(GBRbp_report), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = GBRbp_report)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("When you visit the GBR how often do you preform the following actions: Report suspicious activity to the authorities (e.g., fishing in no-take or ‘green’ zones, dumping rubbish)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

### Question 19

```{r}
# Histogram for Support of MPAs

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_zoning), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>
  
  # Plot Data
  ggplot(aes(x = inter_zoning)) +
  
  # Convert raw count into percentage of respondents 
  geom_histogram(aes(y = after_stat(count / sum(count) * 100)),
                 
  # Set spacing and color scheme               
  binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:10) +
  
  # Format the y-axis labels 
  scale_y_continuous(labels = scales::label_percent(scale = 1)) +
  
  # Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
  # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Marine Park zoning to restrict certain activities (e.g. fishing, collecting) in some areas of the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Percentage of Respondents"  
  )
```


```{r}
# Histogram for Support of Fish Closures

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_fishclosures), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_fishclosures)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Seasonal closures for certain fish species (e.g., closures during spawning)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Culling CoTS

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_culling), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_culling)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Culling Crown of Thorns Starfish (a sea star that feeds on coral) to protect corals on reefs", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Coral Restoration

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_coralrestore), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_coralrestore)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Coral restoration (i.e., assisted propagation or ‘gardening’ of corals) to replenish damaged reefs", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Citizen Science Programs

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_citizen), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_citizen)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Community and citizen science programs that involve local people in reef monitoring and clean-ups", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Mangrove & Seagrass Restoration

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_coastrestore), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_coastrestore)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Coastal and inshore restoration (e.g., mangroves, seagrass)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Island Restoration

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_islandrestore), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_islandrestore)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Island rehabilitation and restoration", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Increased Poaching Enforcement

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_illfish), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_illfish)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Surveillance and enforcement to reduce illegal fishing (e.g., poaching in protected Marine Park zones)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Assisted Coral Adaptation

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_coraladapt), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_coraladapt)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Assisted coral adaptation to increase tolerance to rising sea temperatures (e.g., through selective breeding of coral)", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Improved Water Quality

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_water), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_water)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Improved land management to reduce sediments and nutrients flowing into the sea", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Reduction in Plastics

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_rubbish), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_rubbish)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Efforts to reduce rubbish and plastics from urban areas entering GBR waters", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Support of Indigenous Rangers

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_indig), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_indig)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Providing support for Indigenous Traditional Owner co-management of the GBR (e.g., Indigenous Rangers, training programs)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for Support of Responsible In-Water Recreation

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_rec), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_rec)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Efforts to improve on-water practices by recreational users and tourists (e.g., reducing coral damage from anchors and human contact)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for Support of Govt Climate Action

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_carbon), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_carbon)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Government and industry initiatives to reduce carbon emissions and tackle climate change", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for Support of Less Invasive Fishing Tech

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(inter_fishing), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = inter_fishing)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning the protection and managment of the GBR, how important do you consider: Development of new equipment (fishing gear) for commercial fishers to reduce risks to non-target species (e.g., threatened and protected animals)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

### Question 21

```{r}
# Histogram for Belief that most people try to reduce impacts

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(desc_norm), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = desc_norm)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements: I think that most people in my local area try to reduce any impacts they might have on the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that local areas have responsibility to reduce impact

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(shared_resp), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = shared_resp)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements: I believe it is the responsibility of everyone in my local area to reduce their impacts on the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief in moral obligation to reduce impact

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(moral_oblig), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = moral_oblig)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements:  I feel morally obligated (i.e., a sense of duty) to reduce any impacts I might personally have on the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that one can't make a personal difference in improving the GBR's health

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(pers_diff), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = pers_diff)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements:  I feel that I cannot make a personal difference in improving the health of the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief in good understanding of things one can do to help the GBR

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(procedural_knowl), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = procedural_knowl)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements: I have a good understanding of the things I can do to help the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for claim that one would change their daily life if it helped the GBR

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(general_motivation), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = general_motivation)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements: I would be willing to make an effort to do something differently in my daily life, if it helped the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for support of current management rules on use and access to GBR

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(support_rules), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = support_rules)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements: I support the current rules and regulations that affect access and use of the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that society has a moral obligation to protect the GBR

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(society_oblig), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = society_oblig)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements: I believe society has a moral obligation (i.e., a duty) to protect the GBR for future generations", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief in social expectation to reduce impacts in local area

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(injunc_norm), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = injunc_norm)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements: In my local area, there is a strong social expectation for people to minimise their impacts on the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that caring for the GBR is part of identity

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(steward_identity), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = steward_identity)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements: Taking actions to look after the GBR is important to the way that I think of myself as a person", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that actions taken to help GBR are recognized by management

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(steward_respect), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = steward_respect)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate your level of agreement with the following statements: The actions I take to look after the GBR are recognised and respected by GBR management", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

### Question 23

```{r}
# Histogram for Understanding how GBR is Managed

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(dm_understanding), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = dm_understanding)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning managment of the GBR, rate your level of agreement with the statment: I have a good understanding of how the GBR is managed", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that GBR is Managed Fairly

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(dm_procfair), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = dm_procfair)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning managment of the GBR, rate your level of agreement with the statment: I think that decisions about managing the GBR are made in a fair way", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that GBR Management Costs are Fairly Distributed

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(dm_distfair), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = dm_distfair)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning managment of the GBR, rate your level of agreement with the statment:  I think that the benefits and costs of managing the GBR are distributed fairly across different groups of people (e.g., GBR residents, tourist operators, fishers)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that GBR Management Costs are Fairly Distributed
# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(dm_understanding), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = dm_understanding)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning managment of the GBR, rate your level of agreement with the statment: I have a good understanding of how the GBR is managed", width = 80),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that GBR Management Respects all Stakeholder Groups

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(dm_equity), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = dm_equity)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning managment of the GBR, rate your level of agreement with the statment:  I believe that all relevant people and groups are recognised and respected in decision-making about GBR management", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that GBRMPA is Trustworthy

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(trust_dm), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = trust_dm)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning managment of the GBR, rate your level of agreement with the statment:  I believe that GBR decision-makers (e.g., the Great Barrier Reef Marine Park Authority) are trustworthy", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Satisfaction in GBR Management

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(sat_mgmt), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = sat_mgmt)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Overall, I feel satisfied with how the GBR is managed", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Personal Benefit from GBR Management

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(benefit_mgmt), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = benefit_mgmt)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning managment of the GBR, rate your level of agreement with the statment: I personally benefit from actions taken to manage the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Belief that GBR Management is well Recognized

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(pride_mgmt), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = pride_mgmt)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning managment of the GBR, rate your level of agreement with the statment:  I believe the GBR is widely recognised as well managed", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

### Question 33

```{r}
# Histogram for Prioritizing Healthy Fish Populations 

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(priority_fish), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = priority_fish)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:3) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning commercial fishing in the GBR which of the following objectives should be the highest priorities? Select your top 3 choices in order of importance with 1 being the most important: Healthy fish populations", width = 70),
    x = "Rating (1-3)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Prioritizing less Bycatch 

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(priority_lowimpact), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = priority_lowimpact)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:3) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning commercial fishing in the GBR which of the following objectives should be the highest priorities? Select your top 3 choices in order of importance with 1 being the most important:  Low impact on non-target species (e.g., avoid using fishing equipment that catches threatened and protected animals)", width = 70),
    x = "Rating (1-3)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Prioritizing Commercial opportunities for Traditional Owners 

 # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(priority_TO), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = priority_TO)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:3) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning commercial fishing in the GBR which of the following objectives should be the highest priorities? Select your top 3 choices in order of importance with 1 being the most important:  Commercial opportunities for Traditional Owners", width = 70),
    x = "Rating (1-3)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Prioritizing Local Supply of Seafood 

 # Filter NA values and sort by fisher status
  raw_data1 |> filter(!is.na(priority_supply), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = priority_supply)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:3) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning commercial fishing in the GBR which of the following objectives should be the highest priorities? Select your top 3 choices in order of importance with 1 being the most important: Local supply of seafood for local communities and seafood businesses", width = 70),
    x = "Rating (1-3)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Prioritizing Jobs for Local Commercial Fishers 

 # Filter NA values and sort by fisher status
  raw_data1 |> filter(!is.na(priority_jobs), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = priority_jobs)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:3) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning commercial fishing in the GBR which of the following objectives should be the highest priorities? Select your top 3 choices in order of importance with 1 being the most important: Jobs for local commercial fishers", width = 70),
    x = "Rating (1-3)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for Prioritizing low impact on Recreational Fishing

 # Filter NA values and sort by fisher status
  raw_data1 |> filter(!is.na(priority_recfishing), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = priority_recfishing)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:3) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Concerning commercial fishing in the GBR which of the following objectives should be the highest priorities? Select your top 3 choices in order of importance with 1 being the most important: Low impact on recreational fishing opportunities", width = 70),
    x = "Rating (1-3)",
    y = "Number of Respondents"
  ) 
```

## Environmental Attitudes

### Question 15

```{r}
# Histogram for value of biodiversity the GBR provides

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_biodiversity), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_biodiversity)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR supports a variety of marine life, such as fish and corals", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of GBR existing despite no personal benefits

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_exist), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_exist)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The fact that the GBR exists, even if I don’t use or benefit from it", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of passing down traditions related to GBR

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_bequest), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_bequest)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR provides a place where people can continue to pass down wisdom, traditions, and a way of life", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of Tourism

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_icon), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_icon)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR attracts people from all over the world", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of World Heritage Status

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_recognition), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_recognition)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR is recognised nationally and internationally for its iconic status (e.g., World Heritage Area)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for value of GBR providing Seafood

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_provision), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_provision)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR provides fresh seafood", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of educational opportunities from GBR

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_science), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_science)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: People can learn about the environment through GBR educational, research, and monitoring activities", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of Traditional Owner Heritage

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_indigenous), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_indigenous)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR has rich Traditional Owner Heritage", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of Maritime Heritage

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_heritage), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_heritage)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR has historic maritime heritage (e.g., shipwrecks)", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of GBR Spiritual/Artistic Inspiration

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_spiritual), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_spiritual)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR provides spiritual meaning and/or artistic inspiration to people", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of GBR supporting local economy

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_economy), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_economy)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR supports the local economy", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of GBR providing social opportunities 

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_social), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_social)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR provides a place for people to connect socially with other people", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of GBR Recreation

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_recreation), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_recreation)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: The GBR provides opportunities for people to engage in recreational activities and tourism", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for value of GBR providing opportunities to be in nature

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(values_ture), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = values_ture)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("How much do you value the following aspect of the GBR: I believe the GBR is widely recognised as well managed", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

### Question 17

```{r}
# Mutate data labels for I don't know category
raw_data <- raw_data |>
  mutate(threat_cots = if_else(threat_cots == 9, 6, threat_cots)) |>
  mutate(threat_fishing = if_else(threat_fishing == 9, 6, threat_fishing)) |>
  mutate(threat_runoff = if_else(threat_runoff == 9, 6, threat_runoff)) |>
  mutate(threat_rubbish = if_else(threat_rubbish == 9, 6, threat_rubbish)) |>
  mutate(threat_cc = if_else(threat_cc == 9, 6, threat_cc)) |>
  mutate(threat_tourism = if_else(threat_tourism == 9, 6, threat_tourism)) |>
  mutate(threat_devt = if_else(threat_devt == 9, 6, threat_devt)) |>
  mutate(threat_ports = if_else(threat_ports == 9, 6, threat_ports)) |>
  mutate(threat_mining = if_else(threat_mining == 9, 6, threat_mining)) |>
  mutate(threat_popn = if_else(threat_popn == 9, 6, threat_popn)) |>
  mutate(threat_mgmt = if_else(threat_mgmt == 9, 6, threat_mgmt)) |>
  mutate(threat_weather = if_else(threat_weather == 9, 6, threat_weather)) |>
  mutate(threat_heatwaves = if_else(threat_heatwaves == 9, 6, threat_heatwaves)) |>
  mutate(threat_bleaching = if_else(threat_bleaching == 9, 6, threat_bleaching)) 
  
#glimpse(raw_data)
```



```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of CoTS as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_cots), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>
    
 

  # Plot Data
  ggplot(aes(x = threat_cots, fill = factor(threat_cots))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Crown of thorns starfish (a sea star that feeds on coral)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of illegal fishing as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_fishing), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_fishing, fill = factor(threat_fishing))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Illegal fishing practices (e.g., exceeding bag limits, poaching in no-take zones))", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of terrestrial runoff as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_runoff), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_runoff, fill = factor(threat_runoff))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Land-based runoff (containing sediment, fertiliser, pesticides, etc.))", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of rubbish and debris as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_rubbish), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_rubbish, fill = factor(threat_rubbish))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Rubbish and marine debris)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of Climate Change as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_cc), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_cc, fill = factor(threat_cc))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Climate change)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of Tourism as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_tourism), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_tourism, fill = factor(threat_tourism))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Tourism)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of Coastal Development as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_devt), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_devt, fill = factor(threat_devt))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR:  Coastal development and land clearing)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of Ports and shipping as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_ports), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_ports, fill = factor(threat_ports))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Ports and shipping)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of mining as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_mining), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_mining, fill = factor(threat_mining))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Mining)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of population growth as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_popn), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_popn, fill = factor(threat_popn))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Population growth)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of governance as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_mgmt), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_mgmt, fill = factor(threat_mgmt))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Governance (i.e., management of the GBR))", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of sever weather as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_weather), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_weather, fill = factor(threat_weather))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Severe weather events (e.g., cyclones, storms, flooding))", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of marine heatwaves as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_heatwaves), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_heatwaves, fill = factor(threat_heatwaves))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Marine heatwaves)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of coral bleaching as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_bleaching), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_bleaching, fill = factor(threat_bleaching))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Coral bleaching", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for rating of CoTS as threat to GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(threat_cots), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = threat_cots, fill = factor(threat_cots))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
    
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Doesn't represent a threat at all",
      "2 = A minor threat",
      "3 = A moderate threat",
      "4 = A serious threat",
      "5 = Extremely serious threat",
      "6 = I don't know")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Rate the extent to which the following issue represents a threat to the GBR: Crown of thorns starfish (a sea star that feeds on coral)", width = 70),
    x = "Responses",
    y = "Number of Respondents"
  ) 
```

### Question 28

```{r}
# Histogram for desire to live in region if GBR declined

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(impact_desire), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = impact_desire)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate you agreement with the following satements: If the health of the GBR significantly declined, living in the GBR region would become undesirable to me", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for financial situation if GBR declined

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(impact_fince), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = impact_fince)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate you agreement with the following satements: If the health of the GBR significantly declined, my financial situation would be negatively affected", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for impact on lifestyle if GBR declined

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(impact_lifestyle), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = impact_lifestyle)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate you agreement with the following satements: If the health of the GBR significantly declined, my lifestyle would be negatively affected", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for physical/mental health decline if GBR declined

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(impact_wellbeing), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = impact_wellbeing)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate you agreement with the following satements: If the health of the GBR significantly declined,my physical and/or mental wellbeing would be negatively affected", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

```{r}
# Histogram for sense of grief if GBR declined

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(impact_grief), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = impact_grief)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Rate you agreement with the following satements: If the health of the GBR significantly declined, I would feel a sense of grief or loss", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  ) 
```

## Misinformation

### Question 18

```{r}
#| fig-width: 10
#| fig-height: 6

# Histogram for certainty that climate change is a threat to the GBR

  # Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(cc_belief), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  
  # Mutate data to add labels to fisher status for graphs
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
 # Add loop to count sample size for each fisher status group and add to facet label
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = cc_belief, fill = factor(cc_belief))) +
  
  # Set spacing and color scheme
  geom_histogram(binwidth = 1, boundary = 0.5, color = "white") +
  
  # Set axis breaks to match the rating scale
  scale_x_continuous(breaks = 1:6) +
  
  # Create Legend for Responses
  scale_fill_manual(
    name = "Rating",
    values = rep("steelblue", 6),
    labels = c(
      "1 = Threat that needs immediate action",
      "2 = Threat but doesn't need immediate action ",
      "3 = Need more evidence to form an opinion",
      "4 = Not a threat",
      "5 = No view",
      "6 = Don't believe in climate change")) +
  
# Facet wrap to separate by fisher status and set free y-axis scaling
  facet_wrap(~ group_label, scales = "free_y") +
  
 # Edit in Long Title for exact question wording, Axis Labels, Theme, etc
  labs(
    title = str_wrap("Which of the following statements best describes your beliefs about climate change and the Great Barrier Reef (GBR)?", width = 70),
    x = "Responses (1-6)",
    y = "Number of Respondents"
  ) 
```

### Question 29
```{r}
# Mutate data labels for I don't know category
raw_data <- raw_data |>
  mutate(threat_cots = if_else(threat_cots == 9, 6, threat_cots)) |>
  mutate(threat_fishing = if_else(threat_fishing == 9, 6, threat_fishing)) |>
  mutate(threat_runoff = if_else(threat_runoff == 9, 6, threat_runoff)) |>
  mutate(threat_rubbish = if_else(threat_rubbish == 9, 6, threat_rubbish)) |>
  mutate(threat_cc = if_else(threat_cc == 9, 6, threat_cc)) |>
  mutate(threat_tourism = if_else(threat_tourism == 9, 6, threat_tourism)) |>
  mutate(threat_devt = if_else(threat_devt == 9, 6, threat_devt)) |>
  mutate(threat_ports = if_else(threat_ports == 9, 6, threat_ports)) |>
  mutate(threat_mining = if_else(threat_mining == 9, 6, threat_mining)) |>
  mutate(threat_popn = if_else(threat_popn == 9, 6, threat_popn)) |>
  mutate(threat_mgmt = if_else(threat_mgmt == 9, 6, threat_mgmt)) |>
  mutate(threat_weather = if_else(threat_weather == 9, 6, threat_weather)) |>
  mutate(threat_heatwaves = if_else(threat_heatwaves == 9, 6, threat_heatwaves)) |>
  mutate(threat_bleaching = if_else(threat_bleaching == 9, 6, threat_bleaching)) 
  
#glimpse(raw_data)
```

### Question 34



### Question 35

```{r}
# Histogram for hope towards the future of the GBR

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(hope), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = hope)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Considering the condition of the GBR, rate your level of agreement with the following statements: All things considered, I feel hopeful about the future of the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for sadness on GBR outlook

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(sad), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = sad)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Considering the condition of the GBR, rate your level of agreement with the following statements: I feel sad when I think about the outlook for the GBR", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for rating of beauty of the GBR

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(aesthetics), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = aesthetics)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Considering the condition of the GBR, rate your level of agreement with the following statements: The aesthetic beauty (i.e., natural beauty) of the GBR is outstanding", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for ratings of GBR health

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(GBRh_overall), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = GBRh_overall)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Considering the condition of the GBR, rate your level of agreement with the following statements: Overall, I think the GBR is currently in good health", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for trust in science of GBR health

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(trust_reefscience), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = trust_reefscience)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Considering the condition of the GBR, rate your level of agreement with the following statements: I trust the science about GBR health", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```

```{r}
# Histogram for tiredness of GBR degradation stories

# Filter NA values and sort by fisher status
  raw_data |> filter(!is.na(reef_fatigue), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                        "Y" = "Recreational Fisher",
                                        "N" = "Non-Fisher")) |>
  group_by(Are_you_a_Rec_Fisher) |>
  mutate(group_label = paste0(Are_you_a_Rec_Fisher, " (n = ", n(), ")")) |>
  ungroup() |>

  # Plot Data
  ggplot(aes(x = reef_fatigue)) +
  geom_histogram(binwidth = 1, boundary = 0.5, fill = "steelblue", color = "white") +
  scale_x_continuous(breaks = 1:10) +
  facet_wrap(~ group_label, scales = "free_y") +
  labs(
    title = str_wrap("Considering the condition of the GBR, rate your level of agreement with the following statements:  I am tired of hearing stories about degradation of the GBR in the media", width = 70),
    x = "Rating (1-10)",
    y = "Number of Respondents"
  )
```




