---
title: "Rec_Fish_Regression"
author: "Ryan Waln"
format: html
editor: visual
---

# Introduction

This file is used to conduct regressional analysis on the survey responses of Recreational fishers from the SELTMP in 2025 to determine if 

```{r, message=FALSE, warning=FALSE, include=FALSE}
# R Setup & housekeeping
knitr::opts_chunk$set(
	echo = TRUE,
	include = TRUE,
	message = FALSE,
	warning = FALSE)

rm(list=ls())
objects()
```

```{r}
# Packages
library("gert")
library("usethis")
library("here")
library("tidyverse")
library("readxl")
library("ordinal")
library("MASS")
library("rcompanion")
library("emmeans")
library("rms")
```

```{r}
# Import Raw Data sheet
raw_data <- read_excel(here::here("Data/SELTMP-2025-GBR-surveydataset_v1-0_RecFishingCLUSTERS_RyanW-Sept-22-2026.xlsx"), sheet = "Raw_Data")

##glimpse(raw_data)
```

```{r}
# Filter Data 
MPAs_data <- raw_data |>
  filter(!is.na(inter_zoning), Are_you_a_Rec_Fisher %in% c("Y", "N")) |>
  mutate(
    Are_you_a_Rec_Fisher = recode(Are_you_a_Rec_Fisher,
                                   "Y" = "Recreational Fisher",
                                   "N" = "Non-Fisher"),
    inter_zoning = factor(inter_zoning, ordered = TRUE)
  )
```

# Test the proportional odds assumption
```{r}
MPAs_data <- MPAs_data |>
  mutate(Fisher_numeric = ifelse(Are_you_a_Rec_Fisher == "Recreational Fisher", 1, 0))

plot.xmean.ordinaly(inter_zoning ~ Fisher_numeric, data = MPAs_data, cr = TRUE)
```

# Run ordinal model
```{r}
ord_model <- clm(inter_zoning ~ Are_you_a_Rec_Fisher, data = MPAs_data, link = "logit")
summary(ord_model)
```

# Predicted probability of each rating, by fisher status
```{r}
# see how both fisher status affect ratings and asymp integer (if 1 is included, likely not significant)
basic_probs <- emmeans(ord_model, ~ Are_you_a_Rec_Fisher | inter_zoning, mode = "prob")
summary(emm_prob)
```

```{r}
# see p values and difference in estimates (effect of non fisher status on rating)
basic_probs |> pairs()
```


# Plot probability of each rating with confidence intervals
```{r}
emmip(ord_model, Are_you_a_Rec_Fisher ~ inter_zoning, mode = "prob", dodge = .5, CIs = TRUE) +
  labs(title = "Predicted Probability of Each MPA Support Rating by Fisher Status",
       x = "Rating (1-10)", y = "Predicted Probability") +
  theme_minimal()
```

# Cumulative probability
```{r}
emm_cum <- emmeans(ord_model, ~ Are_you_a_Rec_Fisher | cut, mode = "cum.prob")
summary(emm_cum)

emmip(ord_model, Are_you_a_Rec_Fisher ~ cut, mode = "cum.prob", CIs = TRUE) +
  labs(title = "Cumulative Probability (rating is equal to or less than X) by Fisher Status",
       x = "Rating Threshold", y = "Probability") +
  theme_minimal()
```

# Exceedance probability
```{r}
emm_exc <- emmeans(ord_model, ~ Are_you_a_Rec_Fisher | cut, mode = "exc.prob")
summary(emm_exc)

emmip(ord_model, Are_you_a_Rec_Fisher ~ cut, mode = "exc.prob", CIs = TRUE) +
  labs(title = "Exceedance Probability (rating is greater than X) by Fisher Status",
       x = "Rating (1-10)", y = "Probability") +
  theme_minimal()
```


