---
title: "Rec_Fish_Regression"
author: "Ryan Waln"
format: html
editor: visual
---

# Introduction

This file is used to conduct ordinal regression analysis on the survey responses of Recreational fishers from the SELTMP in 2025. Regressions test trends between support for MPAs against responses to other survey questions and demographics

```{r, message=FALSE, warning=FALSE, include=FALSE}
# R Setup & housekeeping
knitr::opts_chunk$set(
	echo = TRUE,
	include = TRUE,
	message = FALSE,
	warning = FALSE)

rm(list=ls())
objects()
```

```{r}
# Packages
library("gert")
library("usethis")
library("here")
library("tidyverse")
library("readxl")
library("ordinal")
library("MASS")
library("rcompanion")
library("emmeans")
library("rms")
```

```{r}
# Import Raw Data sheet
raw_data <- read_excel(here::here("Data/SELTMP-2025-GBR-surveydataset_v1-0_RecFishingCLUSTERS_RyanW-Sept-22-2026.xlsx"), sheet = "Raw_Data")

##glimpse(raw_data)
```

```{r}
# Filter Data for only Rec Fishers
fisher_data <- raw_data |>
  filter(!is.na(inter_zoning), Are_you_a_Rec_Fisher == "Y") |>
  mutate(inter_zoning = factor(inter_zoning, ordered = TRUE))

# Set up variable to run regression against
fisher_data <- fisher_data |>
  mutate(
  educ = factor(educ, levels = 1:7, ordered = FALSE)            # use for categorical question
  # q_b = as.numeric(q_a)       # use for numeric question
  ) |>
  drop_na(educ)
```

## Test the proportional odds assumption

```{r}
# Change column to to numerical binary
fisher_data |>
  mutate(Fisher_numeric = ifelse(Are_you_a_Rec_Fisher == "Recreational Fisher", 1, 0))

# Set up model (can add in other predictors w/ +)
ord_full <- clm(inter_zoning ~ educ, data = fisher_data, link = "logit")

# Test for violation of proportional odds
nominal_test(ord_full)

# Plot results
plot.xmean.ordinaly(inter_zoning ~ educ, data = fisher_data, cr = TRUE)
```

## Run ordinal regression model

```{r}
# One predictor at a time 
ord_educ <- clm(inter_zoning ~ educ, data = fisher_data, link = "logit")
summary(ord_educ)

# Multiple predictors together
#ord_full <- clm(inter_zoning ~ q_a + q_b + q_c, data = fisher_data, link = "logit")
#summary(ord_full)

# Odds ratios with 95% CIs
exp(cbind(OR = coef(ord_full), confint(ord_full)))

# Test whether each predictor improves the model overall
#drop1(ord_full, test = "Chisq")

# Compare models
#anova(ord_educ, ord_full)
```

## Predicted probability of each rating, by fisher status

```{r}
# see how education level affects ratings and asymp integer (if 1 is included, likely not significant)
educ_probs <- emmeans(ord_educ, ~ educ | inter_zoning, mode = "prob")
summary(educ_probs)
pairs(educ_probs)
```
## Plot probability of each rating with confidence intervals

```{r}
emmip(ord_educ, educ ~ inter_zoning, mode = "prob", dodge = 1.5, CIs = TRUE) +
  labs(title = str_wrap("Predicted Probability of MPA Support Rating by Education Level", width = 30),
       x = "Rating (1-10)", y = "Predicted Probability")
```

## Cumulative probability

```{r}
# Cumulative probability of ratings by education level
educ_cumm <- emmeans(ord_educ, ~ educ | cut, mode = "cum.prob")
summary(educ_cumm)
pairs(educ_cumm)

emmip(ord_educ, educ ~ cut, mode = "cum.prob", dodge = 1.5, CIs = TRUE) +
  labs(title = str_wrap("Cumulative Probability (rating is equal to or less than X) by Education Level", width = 30),
       x = "Rating Threshold", y = "Cumulative Probability")
```

## Exceedance probability

```{r}
# Exceedance probability of ratings by education level
educ_ex <- emmeans(ord_educ, ~ educ | cut, mode = "exc.prob")
summary(educ_ex)
pairs(educ_ex)

emmip(ord_educ, educ ~ cut, mode = "exc.prob", dodge = .5, CIs = TRUE) +
  labs(title = str_wrap("Exceedance Probability of MPA Support Rating by Education Level", width = 30),
       x = "Rating Threshold", y = "Exceedance Probability")
```

